Modular Synthesis of Verified Verifiers of Computation with STV Algorithms

### 2019-03-14 paper/paper.tex
my revisions almost done fully

\begin{IEEEkeywords}

\end{IEEEkeywords}
\section{Introduction}\label{sec:intro}
%\setlength{\abovedisplayskip}{0.5em}
%\setlength{\belowdisplayskip}{0.5em}
Single transferable vote (STV)\cite{DFar} is a preferential voting scheme used in various jurisdictions around the world, including Ireland, Malta, India, Pakistan, Australia, New Zealand and some municipalities of the United States, typically for multi-seat constituencies.  A ballot is a preference-ordered list of candidates, typically obtained specifying a numerical preference for each candidate appearing on the ballot paper.
% as illustrated in Figure
%\footnote{DP: remove figure and explain textually if low on space}
%\ref{fig:ballot}.

@@

The semantics of each machine transition label consists of conjunctions of formally specified general pre- and post-conditions across STV schemes which enforce when and how to take a tallying action and what the immediate effect is. To demonstrate the process of specification, implementation and verification of the machine transitions and their semantics, we discuss the transfer-elect transition.

STV schemes \emph{explicitly} declare four conditions that must be satisfied  for any legitimate application of transfer-elect; 
\begin{itemize}
\item[a.] there are still vacancies to fill
\item[b.] There are no uncounted ballots to deal with
%\item[c.] no more continuing candidate other than already elected has reached or exceeded the quota
\item[c.] there is no vote from any eliminated candidate still awaiting distribution, and
\item[d.] there are surplus votes of elected candidates to  transfer.
\end{itemize}

Also there are some \emph{implicit} conditions present in legal documents describing transfer-elect. These constraints come to attention either as the result of a straightforward understanding of the explicit conditions above or as   auxiliary components that are taken for granted by legislators but are
necessary for proper functioning of the explicit constraints;
\begin{enumerate}
\item every candidate in the pre- and post-state of transfer-elected has a unique tally and pile
\item no one is elected or eliminated by applying transfer-elect
\item no candidate attracts any new vote by transfer-elect and therefore tallies remain the same
\item candidates whose names appears in the backlog of elected are indeed among elected candidates
\item any elected candidate is no longer a continuing candidate so that they do not receive votes any further
\item the list of competing candidates in the election is not empty and has no duplication of names
\end{enumerate}  
Conjunctions of formal declarations of the above explicit and implicit conditions form the semantics of the transition label transfer-elect.   The predicate TransferAuxSpec defines  the semantics of this transition.
 \begin{small}
\begin{holthmenv}
  \HOLConst{TransferAuxSpec}\;(\HOLFreeVar{qu}\HOLSymConst{,}\HOLFreeVar{st}\HOLSymConst{,}\HOLFreeVar{l})\;\HOLFreeVar{ba}\;\HOLFreeVar{t}\;\HOLFreeVar{t\sp{\prime}}\;\HOLFreeVar{p}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{bl}\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLFreeVar{e}\;\HOLFreeVar{e\sp{\prime}}\;\HOLFreeVar{h}\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{\HOLTokenEquiv{}}\\
\;\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenNotEqual{}}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{ba}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{t\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{e\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{length}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{st}\;\HOLSymConst{\HOLTokenConj{}}\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{t}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\\\;\;\HOLConst{ValidInitCandList}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}
\;\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{p})
\end{holthmenv}
\end{small}

@@

We implement for each of the above declarations a counterpart computational \underline{dec}ision procedure that is later translated and then extracted as part of the verifier for actual computation. To illustrate how this phase proceeds, we provide some instances. The following two functions together implement Valid\textunderscore{}PileTally.

@@

\item[$\bullet_{5}$] pile of the candidate whose surplus is transferred is emptied in the post-state of transfer-elect.

@@

We augment the formal counterparts of the $\bullet_{i}$ conditions  to the clauses given in Section~\ref{sec:MachineSem} to obtain the specification TransferActSpec for transfer-elect of ACT STV.  

@@

The lines denoted by the star symbol~($\star$) in Definition of TransferActSpec formalise the Clause~$\bullet_{7}$ above. Also note that we place the last parcel of the pile of the candidate $c$ whose votes are transferred first into the list of uncounted ballots so that in the subsequent transition count deals with distributing the votes and ``recalculating'' candidates' tallies and piles. Finally, because of efficiency purposes our system is designed to update the fractional transfer value of the surplus in formalisation of the elect transition instead of the transfer-elected transition.

We next define computational twins for the components of TransferActSpec and use them to implement a computational counterpart for the semantics of the ACT transfer-elect. 

@@

We have already completed the verifiers synthesis process for five different STV algorithms\footnote{see  \url{https://github.com/MiladKetabGhale/Modular_Checker}}. Here,  we only discuss instantiation of the transfer-elect  based on the  CADE STV~\cite{cade}. As we have already illustrated how a specification and the corresponding implementation of an algorithm advance, we therefore only elaborate on how CADE STV varies from ACT STV in textual descriptions of its  semantics and subsequently its implementations.

@@

\item[$\star_{3}$] backlog of the elected candidates is emptied in the post-state of transfer-elect.
\item[$\star_{4}$] the election \underline{restarts} after each round of transfer-elect.

@@

\item[$\star_{4c}$] the eliminated candidates are ``resurrected'' meaning they start to be continuing candidates in the post-state.  

@@

\;\HOLBoundVar{tbl}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{ba\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{APPEND_ALL}\;\HOLFreeVar{p}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\;\;\HOLSymConst{\HOLTokenNeg{}}\HOLConst{null}\;(\HOLConst{getCandPile}\;\HOLBoundVar{hbl}\;\HOLFreeVar{p})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{ALL_EMPTY}\;\HOLFreeVar{l}\;\HOLFreeVar{p\sp{\prime}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{l}\\

@@

@@

In this section, when we instantiated transitions of the machine, particularly transfer-elected, we named instantiations differently. For example, we represented instantiation of transfer-elected with the ACT STV by  Transfer\underline{Act}Dec. This choice was out of pedagogical purposes to assist the reader with understanding the work. In actual engineering however we practice a sensible alternative. We carry out different instantiations of the machine in separate modules but uniformly name instantiations of the transitions. For example, for instantiation of the machine with the ACT STV, we have a module accordingly named and inside the module we refer, for instance, to instantiation of transfer-elect as TransferDec or TransferSpec without the infix Act.

@@

There is work which formally verify some STV algorithms in the theorem prover Coq. Ghale~et~al~\cite{Ghale:2017:FVS} formalise the student union STV algorithm used in some union elections Australia. Pattinson and Schurmann~\cite{DBLP:conf/ausai/PattinsonS15} verify the ``vanilla'' STV algorithm.   Pattinson and Tiwari~\cite{DBLP:conf/itp/PattinsonT17} prove the Schultz voting scheme correct, and Verity and Pattinson~\cite{DBLP:conf/acsw/VerityP17} verify an invariant of STV. Finally, Ghale~et~al~\cite{} provide a modular treatment of formalisation and verification of STV algorithms. They all then employ the automatic program extraction tool of Coq to obtain Haskell or OCaml programs to provably correctly compute election results based on the algorithm for any real input data. These programs output verifiable evidence upon each execution. Some of them~\cite{DBLP:conf/ausai/PattinsonS15,DBLP:conf/itp/PattinsonT17}    
 implement a verifier for checking the correctness of execution instances. However, the verifier is not verified. They implement their verifier as Haskell programs without proving that the verifier itself computes correctly. Moreover, even trusting that the verifier is reliable, there remains other unverified layers to trust in. For example, they rely on the GHC compiler to execute the program in the operating system. As GHC is not a verified compiler one has to trust that the executable machine code also behaves correctly.

>>>>

\begin{IEEEkeywords}
Framework, Modularity, Single Transferable Voting, Algorithms, Veriable Computation, Proof Engineering, Code Synthesis, Elections, Trustworthiness, Transparency 
\end{IEEEkeywords}
\section{Introduction}\label{sec:intro}
%\setlength{\abovedisplayskip}{0.5em}
%\setlength{\belowdisplayskip}{0.5em}
Single transferable vote (STV)\cite{DFar} is a preferential voting scheme used in various jurisdictions around the world, including Ireland, Malta, India, Pakistan, Australia, New Zealand and some municipalities of the United States, typically for multi-seat constituencies.  A ballot is a preference-ordered list of candidates, typically obtained specifying a numerical preference for each candidate appearing on the ballot paper.
% as illustrated in Figure
%\footnote{DP: remove figure and explain textually if low on space}
%\ref{fig:ballot}.

@@

The semantics of each machine transition label consists of conjunctions of formally specified general pre- and post-conditions across STV schemes which enforce when and how to take a tallying action and what the immediate effect is. To demonstrate the process of specification, implementation and verification of the machine transitions and their semantics, we discuss the transfer-elected transition.

STV schemes \emph{explicitly} declare four conditions that must be satisfied  for any legitimate application of transfer-elected; 
\begin{itemize}
\item[a.] there are still vacancies to fill
\item[b.] There are no uncounted ballots to deal with
%\item[c.] no more continuing candidate other than already elected has reached or exceeded the quota
\item[c.] there is no vote from any eliminated candidate still awaiting distribution, and
\item[d.] there are surplus votes of elected candidates to  transfer.
\end{itemize}

Also there are some \emph{implicit} conditions present in legal documents describing transfer-elected. These constraints come to attention either as the result of a straightforward understanding of the explicit conditions above or as   auxiliary components that are taken for granted by legislators but are
necessary for proper functioning of the explicit constraints;
\begin{enumerate}
\item every candidate in the pre- and post-state of transfer-elected has a unique tally and pile
\item no one is elected or eliminated by applying transfer-elected
\item no candidate attracts any new vote by transfer-elect and therefore tallies remain the same
\item candidates whose names appears in the backlog of elected are indeed among elected candidates
\item any elected candidate is no longer a continuing candidate so that they do not receive votes any further
\item the list of competing candidates in the election is not empty and has no duplication of names
\end{enumerate}  
Conjunctions of formal declarations of the above explicit and implicit conditions form the semantics of the transition label transfer-elected.   The predicate TransferAuxSpec defines  the semantics of this transition.
 \begin{small}
\begin{holthmenv}
  \HOLConst{TransferAuxSpec}\;(\HOLFreeVar{qu}\HOLSymConst{,}\HOLFreeVar{st}\HOLSymConst{,}\HOLFreeVar{l})\;\HOLFreeVar{ba}\;\HOLFreeVar{t}\;\HOLFreeVar{t\sp{\prime}}\;\HOLFreeVar{p}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{bl}\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLFreeVar{e}\;\HOLFreeVar{e\sp{\prime}}\;\HOLFreeVar{h}\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{\HOLTokenEquiv{}}\\
\;\;\HOLFreeVar{bl\sb{\mathrm{2}}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenNotEqual{}}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{ba}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sb{\mathrm{2}}\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{t\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{t}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{e\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLFreeVar{h\sp{\prime}}\;\HOLSymConst{=}\;\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{length}\;\HOLFreeVar{e}\;\HOLSymConst{\HOLTokenLt{}}\;\HOLFreeVar{st}\;\HOLSymConst{\HOLTokenConj{}}\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;(\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{d}.\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{bl}\;\HOLSymConst{\HOLTokenImp{}}\;\HOLConst{\HOLConst{mem}}\;\HOLBoundVar{d}\;\HOLFreeVar{l})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLFreeVar{h}\;\HOLSymConst{\HOLTokenDoublePlus}\;\HOLFreeVar{e})\;\HOLSymConst{\HOLTokenConj{}}\\
\;\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{t}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{Valid_PileTally}\;\HOLFreeVar{p\sp{\prime}}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}\\\;\;\HOLConst{ValidInitCandList}\;\HOLFreeVar{l}\;\HOLSymConst{\HOLTokenConj{}}
\;\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{t})\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{distinct}\;(\HOLConst{map}\;\HOLConst{fst}\;\HOLFreeVar{p})
\end{holthmenv}
\end{small}

@@

We implement for each of the above declarations a counterpart 
%computational 
\underline{dec}ision procedure that is later translated and then extracted as part of the verifier for actual computation. To illustrate how this phase proceeds, we provide some instances. The following two functions together implement Valid\textunderscore{}PileTally.

@@

\item[$\bullet_{5}$] pile of the candidate whose surplus is transferred is emptied in the post-state of transfer-elected.

@@

We augment the formal counterparts of the $\bullet_{i}$ conditions  to the clauses given in Section~\ref{sec:MachineSem} to obtain the specification TransferActSpec for transfer-elected of ACT STV.  

@@

The lines denoted by the star symbol~($\star$) in TransferActSpec formalise the Clause~$\bullet_{7}$ above. Also note that we place the last parcel of the pile of the candidate $c$ whose votes are transferred first into the list of uncounted ballots so that in the subsequent transition count deals with distributing the votes and ``recalculating'' candidates' tallies and piles. Finally, because of efficiency purposes our system is designed to update the fractional transfer value of the surplus in formalisation of the elect transition instead of the transfer-elected transition.

We next define computational twins for the components of TransferActSpec and use them to implement a computational counterpart for the semantics of the ACT transfer-elected. 

@@

To exemplify the flexibility of our framework, we discuss an instantiation of the machine with the CADE STV as well. We refer the reader to our source code\footnote{see  \url{https://github.com/MiladKetabGhale/Modular_Checker}} for details of five other STV instances for which we have successfully completed the verifiers synthesis process. 
%We have already completed the verifiers synthesis process for five different STV algorithms\footnote{see  \url{https://github.com/MiladKetabGhale/Modular_Checker}}. Here,  we only discuss instantiation of the transfer-elect  based on the  CADE STV~\cite{cade}.
As we have already illustrated how a specification and the corresponding implementation of an algorithm advance, we therefore only elaborate on how CADE STV varies from ACT STV in textual descriptions of its  semantics and subsequently its implementations.

@@

\item[$\star_{3}$] backlog of the elected candidates is emptied in the post-state of transfer-elected.
\item[$\star_{4}$] the election \underline{restarts} after each round of transfer-elected.

@@

\item[$\star_{4c}$] the eliminated candidates are ``resurrected'' meaning they start to be continuing candidates in the post-state~(implemented by the ListDiff function below).  

@@

\;\HOLBoundVar{tbl}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLFreeVar{bl\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{\ensuremath{[\,]}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLSymConst{\HOLTokenNeg{}}\HOLConst{null}\;(\HOLConst{getCandPile}\;\HOLBoundVar{hbl}\;\HOLFreeVar{p})\;\HOLSymConst{\HOLTokenConj{}}\\\;\;\;\;\HOLFreeVar{ba\sp{\prime}}\;\HOLSymConst{=}\;\HOLConst{APPEND_ALL}\;\HOLFreeVar{p}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{ALL_EMPTY}\;\HOLFreeVar{l}\;\HOLFreeVar{p\sp{\prime}}\;\HOLSymConst{\HOLTokenConj{}}\;\HOLConst{ListDiff}\;\HOLFreeVar{e\sp{\prime}}\;\HOLFreeVar{h\sp{\prime}}\;\HOLFreeVar{l}\\

@@

%The function ListDiff implements the Clause~$_{4c}$.
%The function ListDiff implements the Clause~$_{4c}$ to ensure only those competing candidates who are not already elected are given chance to compete again.
%The function ListDiff above checks if the list of continuing candidates in the post state \textsf{h'} consists of all of the competing candidates except those who are already elected~(Clause~$_{4c}$).

@@

In this section, when we instantiated transitions of the machine, particularly transfer-elected, we named instantiations differently. For example, we represented instantiation of transfer-elected with the ACT STV by  Transfer\underline{Act}Dec. This choice was out of pedagogical purposes to assist the reader with understanding the work. In actual engineering however we practice a sensible alternative. We carry out different instantiations of the machine in separate modules but uniformly name instantiations of the transitions. For example, for instantiation of the machine with the ACT STV, we have a module accordingly named and inside the module we refer, for instance, to instantiation of transfer-elected as TransferDec or TransferSpec without the infix Act.

@@

There is work which formally verify some STV algorithms in the theorem prover Coq. Ghale~et~al~\cite{Ghale:2017:FVS} formalise the student union STV algorithm used in some union elections Australia. Pattinson and Schurmann~\cite{DBLP:conf/ausai/PattinsonS15} verify the ``vanilla'' STV algorithm.   Pattinson and Tiwari~\cite{DBLP:conf/itp/PattinsonT17} prove the Schultz voting scheme correct, and Verity and Pattinson~\cite{DBLP:conf/acsw/VerityP17} verify an invariant of STV. Finally, Ghale~et~al~\cite{} provide a modular treatment of formalisation and verification of STV algorithms. They all then employ the automatic program extraction tool of Coq to obtain Haskell or OCaml programs to provably correctly compute election results based on the algorithm for any real input data. These programs output verifiable evidence upon each execution. Some of them~\cite{DBLP:conf/ausai/PattinsonS15,DBLP:conf/itp/PattinsonT17}    
 implement a verifier for checking the correctness of execution instances. However, the verifier is not verified. They implement their verifier as Haskell programs without proving that the verifier itself computes correctly. Moreover, even trusting that the verifier is reliable, there remains other unverified layers to trust in. For example, they rely on the GHC compiler to execute the program. As GHC is not a verified compiler one has to trust that the machine code executed also behaves correctly.
